%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  % \cventry
  %   {Software Architect} % Job title
  %   {Omnious. Co., Ltd.} % Organization
  %   {Seoul, S.Korea} % Location
  %   {Jun. 2017 - May. 2018} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Provisioned an easily managable hybrid infrastructure(Amazon AWS + On-premise) utilizing IaC(Infrastructure as Code) tools like Ansible, Packer and Terraform.}
  %       \item {Built fully automated CI/CD pipelines on CircleCI for containerized applications using Docker, AWS ECR and Rancher.}
  %       \item {Designed an overall service architecture and pipelines of the Machine Learning based Fashion Tagging API SaaS product with the micro-services architecture.}
  %       \item {Implemented several API microservices in Node.js Koa and in the serverless AWS Lambda functions.}
  %       \item {Deployed a centralized logging environment(ELK, Filebeat, CloudWatch, S3) which gather log data from docker containers and AWS resources.}
  %       \item {Deployed a centralized monitoring environment(Grafana, InfluxDB, CollectD) which gather system metrics as well as docker run-time metrics.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\cventry
{Principal Member of the Technical Staff} % Job title
{Sandia National Laboratories} % Organization
{Livermore, CA} % Location
{August 2011 - Current} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Component lead of a multi-disciplinary team of 20 engineers to execute and delivery on a \$200M critical laboratory program. Execution included design, testing, qualification, procurement, quality, production, scheduling and budgeting as well as design and qualification of production hardware testers. The final product included mechanical housings, analog and digital circuitry and firmware.}
    \item {Lead multiple R\&D research programs ranging from \$2.5M to \$5M responsible for developing solutions to DOE and DOD problems. One of these project became the aforementioned \$200M program.}
    \item {Investigated and analyzed error correcting codes under asymmetric channel models with applications to free-space optical communication.}
    \item {Led a 3-year \$1.5M R\&D program investigating the use of compressed sensing for compression of telemetry data. Research included applications of dictionary learning to find optimal data representations as well as using auto-encoders for sparse feature extraction.}
    \item {Led a 2-year \$250K early-career R\&D effort investigating jam resistant communications via modulation design focusing on lattice-based techniques.}
    \item {Analyzed and developed probabilistic models for intrusion detection problems. Performed optimization on these models to develop sensor fusion algorithms.}
    \item {Performed Monte Carlo modeling for SNR analysis of short range mid-UV communications channels.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Systems Engineering Intern} % Job title
{Northrop Grumman} % Organization
{San Diego, CA} % Location
{June 2010 - April 2011} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Developed RF signal direction finding algorithm incorporating real-time and off-line digital signal processing written in MATLAB and LabView}
    \item {Built functional prototype hardware for RF signal detection system}
    \item {Designed antenna interface unit for prototype system including microwave electronics}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Systems Engineering Intern} % Job title
{Qualcomm} % Organization
{San Diego, CA} % Location
{June 2006 - December 2006} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Developed end-to-end rate adaption algorithm for uplink and downlink mobile-to-mobile real-time video transfer}
    \item {Implemented cellular network simulations in C++ and MATLAB}
    \item {Implemented video QoS simulations in MATLAB}
  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
